---
title: "What a wonderful 'wordle'!"
author: "Ramakant"
date: '2022-04-05'
slug: what-a-wonderful-wordle
categories: R
tags: wordle
subtitle: Naa Modati Post
summary: ''
authors: []
lastmod: '2022-04-05T16:15:24+05:30'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

Who ever thought that a bunch of black and green boxes would bring out the <a href = "https://www.merriam-webster.com/dictionary/logophile">logophile</a> in us all? With friends and family groups sharing their progress, I find this to be an entertaining mind-puzzle to kickstart the day. 

And I was not alone in fascination for 5 letter words. Wordle has tickled the fascination of many in the data science community. I found Arthur Holtz's lucid breakdown of the Wordle dataset  <a href = "https://rviews.rstudio.com/2022/02/21/wordle-data-analysis/">post</a> quite interesting. Of course, there is 3B1B's incredibly detailed videos on applying Information Theory to this 6-by-5 grid. (original video as well as the follow-up errata)


```{r EDA_begins, echo = FALSE, warning=FALSE }

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

suppressMessages({ library(httr)
library(dplyr)
library(stringr)
library(ggplot2)
library(ggthemes)
library(scales)
library(tidyr)
})

url <- "https://www.nytimes.com/games/wordle/main.18637ca1.js"
wordle_script_text <- GET(url) %>% 
  content(as = "text", encoding = "UTF-8")
word_list = substr(
  wordle_script_text,
  # cigar is the first word
  str_locate(wordle_script_text, "cigar")[,"start"],
  # shave is the last word
  str_locate(wordle_script_text, "shave")[,"end"]) %>%
  str_remove_all("\"") %>%
  str_split(",") %>%
  data.frame() %>%
  select(word = 1) %>%
  mutate(word = toupper(word))

```

This is an example of the glimpse function
```{r, echo=FALSE}
glimpse(word_list)


```

